This PDF is a Git Repository\\Containing its Own \LaTeX\ Source

### 2017-05-02 article.tex
Added a quote

I hope you like Soviet holes, dear neighbor, because chasing this
rabbit might remind you of \includegraphics{kolskaya}. If you
grew bored reading Tristram Shandy, it's safe to skip to the next
section, 'cause it's turtles all the way down.

@@

Okay, the next step is to figure out the ``chunk'' format.  The chunk
header is variable length, and can be as small as one byte. It encodes
the type of object and the \emph{uncompressed} size of the object. If
the object is a \textit{delta} (\textit{i.e.}, a diff, as opposed to a
complete object), the header is followed by either the SHA-1 hash of
the base object to which the delta should be applied, or a byte
reference within the packfile for the start of the base object. The
remainder of the chunk consists of the object data, zlib-compressed.

@@

\end{tikzpicture}}
\end{center}
This example header represents an object of type \texttt{0b011}, which
happens to be a git blob, and an \emph{uncompressed} length of
$(100_2\,\verb|<<|\,14) +
(1010110_2\,\verb|<<|\,7) + 1001001_2
= 76617$ bytes.  Since this is not a delta object, it is immediately
followed by the zlib-compressed object data.

>>>>

I hope you like Soviet holes, dear neighbor, because chasing this
rabbit might remind you of \includegraphics{kolskaya}. I think it is
useful to describe the git packfile format here, since it is not well
documented elsewhere. If that doesn't interest you, it's safe to skip
to the next section.

@@

Okay, the next step is to figure out the ``chunk'' format.  The chunk
header is variable length, and can be as small as one byte. It encodes
the object's type and its \emph{uncompressed} size. If the object is
a \textit{delta} (\textit{i.e.}, a diff, as opposed to a complete
object), the header is followed by either the SHA-1 hash of the base
object to which the delta should be applied, or a byte reference
within the packfile for the start of the base object. The remainder of
the chunk consists of the object data, zlib-compressed.

@@

\end{tikzpicture}}
\end{center}
The second through fourth most significant bits of the first byte are
used to store the object type. The remainder of the bytes in the
header are of the same format as bytes two and three in this
example. This example header represents an object of type $11_2$,
which happens to be a git blob, and an \emph{uncompressed} length of
$(100_2\,\verb|<<|\,14) + (1010110_2\,\verb|<<|\,7) + 1001001_2 =
76617$ bytes.  Since this is not a delta object, it is immediately
followed by the zlib-compressed object data. The header does not
encode the \emph{compressed} size of the object, since the DEFLATE
encoding can determine the end of the object as it is being
decompressed.

At this point, if you found The Life and Opinions of Tristram Shandy
to be boring or frustrating, then it's probably best to skip to the
next section, 'cause it's turtles all the way down.

{\fontfamily{jkpvos}\selectfont\begin{center}
\begin{tikzpicture}
\node at (0,0) (text) {\begin{minipage}{0.8\hsize}\small
To come at the exact weight of things= in the scientific steel-yard, the fulchrum, [Walter Shandy] would say, should be almost invisible, to avoid all friction from popular tenets=,---without this= the minutiae of philosophy, which should always= turn the balance, will have no weight at all---Knowledge, like matter, he would affirm, was= divisible in infinitum---that the grains= and scruples= were as= much a part of it, as= the gravitation of the whole world.
\end{minipage}};
\node[anchor=north east] at (text.north west) {\LARGE``};
\node[anchor=south west] at (text.south east) {\LARGE''};
\end{tikzpicture}
\end{center}}
